Beam-Helicity and Charge Asymmetries \\ in the Bethe-Heitler and DVCS processes on \\ an Unpolarised Proton Target \underline{Paper Tag: PDVCS (v0.9)} \underline{Drafting Committee: DC90 (\today)}

### 2011-04-01 results.tex
updated 2d plots figs 6 and 7
Made changes suggested by Delia

\begin{figure}
 \begin{center}
 \includegraphics[width=15cm]{bsadvcsplots_eml_par13_bin6_release_all_pic_update}
  \caption{The $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{LU,DVCS}}^{\sin\phi}$ and
$A_{\textrm{LU,I}}^{\sin(2\phi)}$ beam-helicity asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes}
from 1996 until 2007. The error bars (bands) represent the statistical
(systematic) uncertainties. An additional 3.2\,\% scale uncertainty is present in the amplitudes due to the imprecision of
the beam polarisation measurement. Theoretical calculations from the model described in \blue{Ref.} \cite{Kum09} are shown as solid and dashed lines. See text for details. The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
  \label{bsa_xbjrange}
 \end{center}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=15cm]{bcaplots_eml_par13_bin6_all_release_pic_update_withassoc}
    \caption{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007. The error bars (bands) represent the statistical (systematic) uncertainties.  Theoretical calculations from the model described in \blue{Ref.} \cite{Kum09} are shown as solid and dashed lines. See text for details. The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
  \label{bca_xbjrange}
 \end{center}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=15cm]{bcaplots_tc_xnjrange_eml_par13_bin6_9607_pic}
    \caption{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007 as a function of $-t$ for three different $x_{\textrm{B}}$ ranges. The error bars (bands) represent the statistical (systematic) uncertainties.}
  \label{bca_xbjrange2}
 \end{center}
\end{figure}

@@

The solid and dashed curves in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show calculations from a global fit of GPDs to experimental data~\cite{Kum09}. The basic model is a minimalist dual representation of GPDs with only (very) weakly entangled skewness and $t$ dependences. In the model, the $t$ dependence is approximated by a physically-motivated Regge dependence. The solid curves represent the model fit without data from experiments \cite{Cam06, Gir08} at Hall A in Jefferson Laboratory; the model fit represented by the dashed curves includes this data. Both fits include the 1996-2005 H{\sc ermes} data. The model incorporates only twist-2 GPDs and so can provide calculations only for the $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ asymmetry amplitudes. All of the amplitudes are well described by the model.

\blue{The dotted curve in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} shows the result of a calculation made from a hybrid quark-diquark model with a Regge term that is included in order to describe accurately parton distribution functions at low $x$ values. The model incorporates fits only to global deep inelastic scattering and elastic data (for the limits and moments of the underlying GPDs) and exclusive data from Jefferson Lab (to describe the skewness dependence). The model is trained in the kinematic domain of the Hall A and B experiments at Jefferson Lab and the extracted underlying physics quantities are used to calculate the asymmetries in the H{\sc ermes} kinematic region. The model fails to describe the presented data; the predictions have consistently smaller magnitudes than the amplitudes presented in this work.

The open crosses in  Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show calculations of the asymmetries using Compton Form Factors extracted in the VGG formalism from experimental data (including the H{\sc ermes} data from 1996-2005). The extraction of the Compton Form Factors is nearly model independent, but cannot be extended byond the H{\sc ermes} kinematic domain. The presented data is well described by the calculations.}

>>>>

\begin{figure}
 \begin{center}
 \includegraphics[width=15cm]{bsadvcsplots_eml_par13_bin6_release_all_pic_update}
  \caption{The $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{LU,DVCS}}^{\sin\phi}$ and
$A_{\textrm{LU,I}}^{\sin(2\phi)}$ beam-helicity asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes}
from 1996 until 2007. The error bars (bands) represent the statistical
(systematic) uncertainties. An additional 3.2\,\% scale uncertainty is present in the amplitudes due to the imprecision of
the beam polarisation measurement. \blue{Solid and dashed lines show model calculations from~\cite{Kum09}; calculations Ref.~\cite{Liu11} are shown as dashed-dotted lines; amplitude values based on fits to data from Ref.~\cite{Gui11} are shown as open crosses.} See text for details. The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
  \label{bsa_xbjrange}
 \end{center}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=15cm]{bcaplots_eml_par13_bin6_all_release_pic_update_withassoc}
    \caption{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007. The error bars (bands) represent the statistical (systematic) uncertainties.  Theoretical calculations from the model described in \blue{Ref.} \cite{Kum09} are shown as solid and dashed lines and amplitude values calculated from fits to data from Ref.~\cite{Gui11} are shown as open crosses. See text for details. The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
  \label{bca_xbjrange}
 \end{center}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=15cm]{bcaplots_tc_xbjrange_eml_par13_bin6_release_pic_update}
    \caption{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007 as a function of $-t$ for three different $x_{\textrm{B}}$ ranges. The error bars (bands) represent the statistical (systematic) uncertainties.}
  \label{bca_xbjrange2}
 \end{center}
\end{figure}

@@

The solid and dashed curves in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show calculations from a global fit of GPDs to experimental data~\cite{Kum09} including information from the colliders at H{\sc era} and H{\sc ermes} and Jefferson Lab. The basic model is a minimalist dual representation of GPDs with only (very) weakly entangled skewness and $t$ dependences. In the model, the $t$ dependence is approximated by a physically-motivated Regge dependence. The solid curves represent the model fit without data from experiments \cite{Cam06, Gir08} at Hall A in Jefferson Laboratory; the model fit represented by the dashed curves includes this data. Both fits include the 1996-2005 H{\sc ermes} data. The model incorporates only twist-2 GPDs and so can provide calculations only for the $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ asymmetry amplitudes. All of the amplitudes are well described by the model.

\blue{The dash-dotted curves in Figs.~\ref{bsa_xbjrange} shows the result of a calculation made from a quark-diquark model with a Regge-inspired term that is included in order to describe accurately parton distribution functions at low $x$ values~\cite{Liu11}. The ``Regge'' term includes contributions that determine the $t$-dependence of the corresponding GPD. The model incorporates fits to global deep-inelastic scattering and elastic data (to account for the $\xi$-independent limits and moments of the underlying GPDs) and exclusive data from H{\sc ermes} and Jefferson Lab (to describe the skewness dependence). The model describes the $t$-projections of the $A^{\sin\phi}_{\textrm{LU}}$ amplitude well, but the projections in the other kinematic variables are not as well described.}

\blue{The open crosses in  Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show calculations of the asymmetries using Compton Form Factors extracted from experimental data (including the H{\sc ermes} data from 1996-2005)~\cite{Gui11}. The extraction of the Compton Form Factors is independent of assumptions made about the shape of the underlying CFFs, but cannot be simply extended beyond the H{\sc ermes} kinematic domain. The presented data is well described by the calculations.}

### 2011-04-01 summary.tex
Made changes suggested by Delia

Beam\blue{-}helicity and beam\blue{-}charge asymmetries in the azimuthal distribution of real photons from leptoproduction on an unpolarised hydrogen target have been presented. These asymmetries were extracted from a new unpolarised hydrogen data set taken during the 2006 and 2007 operating period of H{\sc ermes}. \blue{An analogous set of asymmetry amplitudes were extracted previously from hydrogen data obtained during the 1996-2005 experimental period as described in Ref.~\cite{Air09}}. A comparison of the amplitudes extracted from these independent data sets have shown that they are compatible and \blue{the }asymmetry amplitudes can therefore be extracted from the complete 1996-2007 event sample. The resulting beam\blue{-}charge asymmetry amplitudes represent the most statistically precise DVCS result that will be published by the H{\sc ermes} collaboration. The result of this extraction of asymmetry amplitudes show that there is a strong signal in the first harmonic of the interference contribution to the beam\blue{-}helicity asymmetry. There are also non zero amplitudes in the zeroth and first harmonic\blue{s} of the beam\blue{-}charge asymmetry. Each of the other higher order asymmetry amplitudes are consistent with zero. The combined results are compared to calculations from ongoing work to fit GPD models to experimental data. \blue{One} model fit~\cite{Kum09} includes the H{\sc ermes} data set from 1996-2005 \blue{shown in} Ref.~\cite{Air09}. The model achieves good agreement with the presented beam-helicity asymmetry amplitude results, and fair agreement with the beam-charge asymmetry amplitudes. \blue{The other model fit does not include the H{\sc ermes} data from 1996-2005 and fails to describe the presented data accurately. A third set of calculations is presented that arise from efforts to extract the Compton Form Factors from experimental data at discrete kinematic points. The fit on which these calculations are based includes the H{\sc ermes} data set from 1996-2005. The calculations describe the data well, but cannot be extrapolated past the H{\sc ermes} kinematic domain.} All \blue{data} amplitudes are also presented \blue{as projections} in $-t$ in bins of $x_{\textrm{B}}$. No localised features are observed in any particular $t$-bin.

>>>>

Beam\blue{-}helicity and beam\blue{-}charge asymmetries in the azimuthal distribution of real photons from leptoproduction on an unpolarised hydrogen target have been presented. These asymmetries were extracted from a new unpolarised hydrogen data set taken during the 2006 and 2007 operating period of H{\sc ermes}. \blue{An analogous set of asymmetry amplitudes were extracted previously from hydrogen data obtained during the 1996-2005 experimental period as described in Ref.~\cite{Air09}}. A comparison of the amplitudes extracted from these independent data sets have shown that they are compatible and \blue{the }asymmetry amplitudes can therefore be extracted from the complete 1996-2007 event sample. The resulting beam\blue{-}charge asymmetry amplitudes represent the most statistically precise DVCS result that will be published by the H{\sc ermes} collaboration. The result of this extraction of asymmetry amplitudes show that there is a strong signal in the first harmonic of the interference contribution to the beam\blue{-}helicity asymmetry. There are also non zero amplitudes in the zeroth and first harmonic\blue{s} of the beam\blue{-}charge asymmetry. Each of the other higher order asymmetry amplitudes are consistent with zero. The combined results are compared to calculations from ongoing work to fit GPD models to experimental data. All \blue{data} amplitudes are also presented \blue{as projections} in $-t$ in bins of $x_{\textrm{B}}$. No localised features are observed in any particular $t$-bin.
